Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2021-12-19 jas_response.tex
Update manuscript with comments

\todo Add to second paragraph of Section 4.3 Numerical example immediately after the sentence: ''In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat e_3)\).``

@@

\todo Use dynamical throughout manuscript

@@

\todo Add to introduction section - replacing the sentence: ''After arrival, a spacecraft will generally spend months or years in a mapping mission phase.``
\begin{correction}
After arrival, space will generally spend upwards of several months in a mapping mission phase~\cite{williams2018,kubota2003,cole1998}.
For example, the recent OSIRIS-REx mission used global imagery to create digital terrain maps over the span of approximately seven months~\cite{williams2018}.

@@

\todo Remove citation ''gates2015`` in the introduction.

\todo add following citations~\cite{williams2018} instead.

@@

\todo Add following after sentence: ''Depending on the mission type, this long period of mapping is curicial to the mission, such as sample collection.``
\begin{correction}
For example, the OSIRIS-REx mission spent approximately seven months in mapping phase where digitial terrain maps and a shape model were constructed in support of main sample collection mission.
\end{correction}

@@

\todo Remove sentence and replace

@@

\todo Correct typo.

@@

\todo Correct typo
This typo has been corrected and the corrected sentence is shown below.

@@

\todo Correct the equation

@@

\todo Copy into paper after equation 19.

@@

\todo Copy into section 4.3. Either the first paragraph or a new second paragraph

@@

\todo Add to paper

@@

\todo Correct in paper

@@

\todo Correct in paper
\begin{correction}
    Areas of high uncertainty are in yellow while areas of low uncertainty are in purple.
    The guidance scheme continually selects regions of high uncertainty until the total shape uncertainty is sufficiently small.
\end{correction}

@@

\todo Correct in paper
\begin{correction}
    The surface cost described here is relatively simple and chosen to be solely a function of the current spacecraft position and shape model.
    Additional scientific criteria such as surface material or location on the body, e.g. equatorial vs. polar regions, can be utilized instead of a random science value as presented here.
\end{correction}

@@

\todo Correct in paper
\begin{correction}
This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require significant computational resources.
\end{correction}

>>>>

@@

@@

\begin{correction}
After arrival, space will generally spend upwards of several months in a mapping mission phase~\cite{williams2018,kubota2003,cole1998}.
For example, the recent OSIRIS-REx mission used global imagery to create digital terrain maps over the span of approximately seven months~\cite{williams2018}.

@@

@@

\begin{correction}
For example, the OSIRIS-REx mission spent approximately seven months in mapping phase where digitial terrain maps and a shape model were constructed in support of main sample collection mission.
\end{correction}

@@

@@

@@

This typo has been corrected and the corrected sentence is shown below.

@@

@@

@@

@@

@@

@@

\begin{correction}
    Areas of high uncertainty are in yellow while areas of low uncertainty are in purple.
    The guidance scheme continually selects regions of high uncertainty until the total shape uncertainty is sufficiently small.
\end{correction}

@@

\begin{correction}
    The surface cost described here is relatively simple and chosen to be solely a function of the current spacecraft position and shape model.
    Additional scientific criteria such as surface material or location on the body, e.g. equatorial vs. polar regions, can be utilized instead of a random science value as presented here.
\end{correction}

@@

\begin{correction}
This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require significant computational resources.
\end{correction}
